### 2016-01-28 Projects/DelCo_2014_2015/Report/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
updated hose stream plotting script and report

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s $\pm15$\%) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
\label{fig:Test_17_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s $\pm15$\%) through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
\\
% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
\textbf{Stream} & 
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
\\ 
\midrule
\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
\\ \multicolumn{6}{c}{} \\
\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
\\ \multicolumn{6}{c}{} \\
\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
\\ \midrule
 & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} \\
\textbf{Stream} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
\multicolumn{3}{c}{} 
\\
\midrule
\textit{Straight} & 1.7 $\pm0.2$ & 1.9 $\pm0.2$ & \multicolumn{3}{c}{} 
\\ \multicolumn{6}{c}{} \\
\textit{Smooth Bore} & 1.7 $\pm0.2$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_18_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
\label{fig:Test_17_BDP_A10_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_19_West_063014_BDP_A10_stream_avgs}
\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}
